\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-07 R/clean_spectral_data.Rmd
species info table

ggplot(distinct(taxons_GT, genusSpecies, .keep_all=TRUE), 
       aes(y = reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", fill = "#7E9E8F") + 
  labs(y = "Taxon code\n",
       x = "\nNumber of spectra") + 
  #theme(axis.text = element_text(size = 12)) +
  theme_bw(base_size=16)

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 9, height = 10)
```

>>>>

ggplot(distinct(taxons_GT, genusSpecies, .keep_all=TRUE), 
       aes(y = reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", fill = "#7E9E8F") + 
  labs(y = "Taxon code\n",
       x = "\nNumber of spectra") + 
  #theme(axis.text = element_text(size = 12)) +
  theme_bw(base_size=14)

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 8, height = 9)
```

### 2020-11-07 analysis/paper/paper.Rmd
species info table

>>>>

```{r taxonTable, message = FALSE, echo = FALSE}
library(knitr)
library(dplyr)

df <- data.frame(taxonCode = c("ABBA", "ABLAL", "ACRU, ACRUR", "ACSAS, ACSA3", 
                               "AMLA", "ARTR2", "BELE", "BENE4", "CACA18", "CAOV2",
                               "CATO6", "CELA", "CODR", "FRAM2", "FRPE", "JUNI", 
                               "JUVIV, JUVI", "LARIX", "LATR2", "LIST2", "LITU",
                               "LOMA6", "MORU2", "NYBI", "NYSY", "PIEN", "PIMA",
                               "PICOL, PICO", "PIEC2", "PIFL2"),
                 scientificName = c("*Abies balsamea*", "*Abies lasiocarpa*", "*Acer rubrum*",
                                    "*Acer saccharum*", "*Amelanchier laevis*", "*Artemisia tridentata*",
                                    "*Betula lenta*", "*Betula neoalaskana*", "*Carpinus caroliniana*",
                                    "*Carya ovata*", "*Carya tomentosa*", "*Celtis laevigata*", 
                                    "*Cornus drummondii*", "*Fraxinus americana*", 
                                    "*Fraxinus pennsylvanica*", "*Juglans nigra*", 
                                    "*Juniperus virginiana*", "*Larix sp.* *",
                                    "*Larrea tridentata*", "*Liquidambar styraciflua*", 
                                    "*Liriodendron tulipifera*", "*Lonicera maackii*",
                                    "*Morus rubra*", "*Nyssa biflora*", "*Nyssa sylvatica*",
                                    "*Picea engelmannii*", "*Picea mariana*", "*Pinus contorta*",
                                    "*Pinus echinata*", "*Pinus flexilis*"),
                 commonName = c("balsam fir", "subalpine fir", "red maple", "sugar maple",
                                "Allegheny serviceberry", "sagebrush", "sweet birch", "resin birch",
                                "American hornbeam", "shagbark hickory", "mockernut hickory",
                                "sugarberry", "roughleaf dogwood", "white ash", "green ash",
                                "black walnut", "eastern redcedar", "larch", "creosote bush",
                                "sweetgum", "tuliptree", "Amur honeysuckle", "red mulberry",
                                "swamp tupelo", "blackgum", "Engelmann spruce", "black spruce",
                                "lodgepole pine", "shortleaf pine", "limber pine"),
                 count = c(47,117, 489, 79, 37, 494, 28, 35, 170, 46, 134, 179, 31, 20, 92, 42, 
                           28, 23, 161, 209, 40, 23, 30, 24, 77, 24, 32, 302, 72, 78))

knitr::kable(x = df, 
             # set column names
             col.names = c("Taxon code",
                           "Scientific name (*species*)",
                           "Common name",
                           "Number of spectra"),
             # center align text in the columns
             align = c("l", "l", "l", "l"),
             format = "simple") 
  # show which rows are grouped together for genus classes visibly in table?

```
